

# Explore FWA Streams
Purpose of this section was to explore the lengths and frequencies of double lined streams as there is a channel width predictor model `channel-width-21`.  Result of this work was that Simon has sampled each double line stream 30 times and kept the average and standard deviation - regarless of segment length [`bcfishpass`](https://github.com/smnorris/bcfishpass/tree/main/01_prep/habitat/02_channel_width).


Load the double line streams used in channel_width_mapped.  In order to facilitate reproducability lets save the streams in a sqlite and pull them back in.
```{r}
shared_dropbox_dir <- "C:/Users/al/Dropbox/New Graph/"
```


```{r eval=FALSE}


##gconnect to database
conn <- DBI::dbConnect(
  RPostgres::Postgres(),
  dbname = dbname_wsl,
  host = host_wsl,
  port = port_wsl,
  user = user_wsl,
  password = password_wsl
)



##get the segments that have a centreline (double line streams)
q <- ("SELECT linear_feature_id, ceil(upstream_route_measure)::integer - floor(downstream_route_measure)::integer AS len,
      watershed_group_code
      FROM whse_basemapping.fwa_stream_networks_sp 
      WHERE edge_type = 1250")

streams <- sf::st_read(conn, query = q) 



##  the streams in a sqlite and pull them back in.
##########################!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!#########################
###change this up so that it matches your version of the shared dropbox!


mydb <- DBI::dbConnect(RSQLite::SQLite(), paste0(shared_dropbox_dir, "fiss/fissr_explore.sqlite"))


conn <- readwritesqlite::rws_connect(paste0(shared_dropbox_dir, "fiss/fissr_explore.sqlite"))
readwritesqlite::rws_write(streams, exists = F, delete = TRUE,
          conn = conn, x_name = "whse_basemapping.fwa_stream_networks_sp")
readwritesqlite::rws_list_tables(conn)
readwritesqlite::rws_disconnect(conn)



```



Load the streams from sqlite.  The table I pull back in after saving as `sqlite` has `linear_feature_id` as integer vs int64 as it was pulled from `postgres`. No issues for this exercise though...

```{r}
conn <- readwritesqlite::rws_connect(paste0(shared_dropbox_dir, "fiss/fissr_explore.sqlite"))
streams <- readwritesqlite::rws_read_table("whse_basemapping.fwa_stream_networks_sp", conn = conn)
readwritesqlite::rws_disconnect(conn)
```

```{r}
summary(streams$len)

```


Lets look at distribution of lengths
```{r}
ggplot(select(streams, len), aes(x=len)) +
  geom_histogram(position="identity", size = 0.75)+
  labs(x = "length", y = "#") +
  ggdark::dark_theme_bw(base_size = 11)

```


```{r}
##segments less than 1000m long
ggplot(select(streams, len) %>% filter(len < 1000), aes(x=len)) +
  geom_histogram(position="identity", size = 0.75)+
  labs(x = "length", y = "#") +
  ggdark::dark_theme_bw(base_size = 11)
```

```{r}
##segments less than 250m long
ggplot(select(streams, len) %>% filter(len < 250), aes(x=len)) +
  geom_histogram(position="identity", size = 0.75)+
  labs(x = "length", y = "#") +
  ggdark::dark_theme_bw(base_size = 11)
```

```{r}
##how many streams are segments are smaller than 50m
streams %>% 
  filter(len > 1000) %>% 
  count()
```

```{r}
streams_equal <- streams %>% 
  mutate(cut = cut_number(len, n = 5)) %>% 
  group_by(cut) %>% 
  summarise(n = n())

streams_equal




```

```{r}
streams_interval <- streams %>% 
  mutate(cut = cut_interval(len, n = 10)) %>% 
  group_by(cut) %>% 
  summarise(n = n())

streams_interval
```

```{r}
streams_length <- streams %>%
  mutate(cut =
           case_when(
             len < 100 ~ '0_100',
             len >= 100 & len < 500 ~ '0100_500',
             len >= 500 & len < 999 ~ '0500_1000',
             len >=999  ~ '1000+')) 

streams_length_sum <- streams_length %>% 
  group_by(cut) %>% 
  summarise(n = n())

streams_length_sum
```


```{r}
ggplot(data = streams_length_sum, mapping = aes(x=cut, y = n)) + 
  geom_bar(stat = "identity") + 
  # ylim(1000, 20000)+
  # labs(x='test') +
  ggdark::dark_theme_bw(base_size = 11)
```


```{r}
ggplot(streams_length, aes(x=len)) +
  geom_histogram(position="identity", size = 0.75)+
  labs(x = "length", y = "#") +
  facet_wrap(~cut, ncol = 2, scales = "free")+
  ggdark::dark_theme_bw(base_size = 11)
```

