

# Explore Data Exported from FISS
Purpose of this section is to explore the species density data provided in csv format from the province.  We would like to be able to tie density of fish species to habitat characteristics including gradient, channel size, discharge, elevation, forest cover, etc.


Load the data from the dropbox


```{r}


shared_dropbox_dir <- "C:/Users/al/Dropbox/New Graph/"


files_to_read <- list.files(paste0(shared_dropbox_dir,"fiss/2020-11-16/"), full.names = T)
files_names <- list.files(paste0(shared_dropbox_dir,"fiss/2020-11-16/"), full.names = F) %>% tools::file_path_sans_ext()


##mini function to change column names to lower case
names_to_lower <- function(dat){
  dat %>% 
  purrr::set_names(nm = stringr::str_to_lower(names(dat)))
}


d <- files_to_read %>% 
  map(readr::read_csv) %>% 
  map(names_to_lower) %>% 
  purrr::set_names(nm = files_names)

```


```{r eval = F}
##pull out the tibbles
details <- d %>% pluck('details')
visits <- d %>% pluck('visits')
habitat <- d %>% pluck('habitat')
counts <- d %>% pluck('counts')
```

Make a table that has all the info we want in one place for the summarized fish

```{r}
d_sum_raw <- left_join(
  d %>% pluck('counts'),
  d %>% pluck('visits'),
  by = 'key'
  ) %>% 
  left_join(
    .,
    d %>% pluck('habitat'),
    by = 'key'
  ) %>% 
##clean it up and grab a density
  filter(!is.na(fishing_area_length) & 
           fishing_area_length > 0 &
           !is.na(fishing_area_width) &
           fishing_area_width > 0 &
           !is.na(utm_easting) &
           !is.na(utm_northing) &
           utm_zone > 0 &
           #For the sake of a first run lets keep only the first passes from sites that have multiple passes
           haul_or_pass == 1 &
           species_code %in% c('RB', 'BT', 'GR', 'CH', 'CO', 'SK', 'WCT', 'ST', 'NFC')) %>%
  mutate(density_100m = number_caught/(fishing_area_length * fishing_area_width) * 100)
  
```




Lets review how many occurrences are from the same site - not sure it matters though.
```{r}
d_same_site <- d_sum_raw %>% 
  group_by(across(data_set:agncy_id)) %>% 
  summarise(n = n()) %>% 
  filter(n > 1)
  
```

<br>

Lets have a look at what we have by species.
```{r}
d_raw_by_sp <- d_sum_raw %>% 
  group_by(species_code) %>% 
  mutate(area = fishing_area_length * fishing_area_width) %>% 
  summarise(n = n(), 
            dens_min = min(density_100m, na.rm = T),
            dens_max = max(density_100m, na.rm = T),
            dens_med = median(density_100m, na.rm = T),
            area_min = min(area, na.rm = T),
            area_max = max(area, na.rm = T),
            area_med = median(area, na.rm = T),
            len_min = min(fishing_area_length, na.rm = T),
            len_max = max(fishing_area_length, na.rm = T),
            len_med = median(fishing_area_length, na.rm = T),
            wid_min = min(fishing_area_width, na.rm = T),
            wid_max = max(fishing_area_width, na.rm = T),
            wid_med = median(fishing_area_width, na.rm = T))

d_raw_by_sp
```


```{r}
ggplot(select(d_sum_raw, fishing_area_length), aes(x=fishing_area_length)) +
  geom_histogram(position="identity", size = 0.75)+
  labs(x = "fishing_area_length", y = "#") +
  ggdark::dark_theme_bw(base_size = 11)

```

```{r}
ggplot(select(d_sum_raw, fishing_area_width), aes(x=fishing_area_width)) +
  geom_histogram(position="identity", size = 0.75)+
  labs(x = "fishing_area_width", y = "#") +
  ggdark::dark_theme_bw(base_size = 11)

```


Lets trim out our strange numbers for the site sizes


```{r}
d_sum <- left_join(
  d %>% pluck('counts'),
  d %>% pluck('visits'),
  by = 'key'
  ) %>% 
  left_join(
    .,
    d %>% pluck('habitat'),
    by = 'key'
  ) %>% 
##clean it up and grab a density
  filter(!is.na(fishing_area_length) & 
           fishing_area_length > 0.9 &
           fishing_area_length < 500.1 &
           !is.na(fishing_area_width) &
           fishing_area_width > 0.5 &
           fishing_area_width < 25.1 &
           !is.na(utm_easting) &
           !is.na(utm_northing) &
           utm_zone > 0 &
           #For the sake of a first run lets keep only the first passes from sites that have multiple passes
           haul_or_pass == 1 &
           species_code %in% c('RB', 'BT', 'GR', 'CH', 'CO', 'SK', 'WCT', 'ST', 'NFC')) %>%
  mutate(density_100m = number_caught/(fishing_area_length * fishing_area_width) * 100)


##have another look at it
d_by_sp <- d_sum %>% 
  group_by(species_code) %>% 
  mutate(area = fishing_area_length * fishing_area_width) %>% 
  summarise(n = n(), 
            dens_min = min(density_100m, na.rm = T),
            dens_max = max(density_100m, na.rm = T),
            dens_med = median(density_100m, na.rm = T),
            area_min = min(area, na.rm = T),
            area_max = max(area, na.rm = T),
            area_med = median(area, na.rm = T),
            len_min = min(fishing_area_length, na.rm = T),
            len_max = max(fishing_area_length, na.rm = T),
            len_med = median(fishing_area_length, na.rm = T),
            wid_min = min(fishing_area_width, na.rm = T),
            wid_max = max(fishing_area_width, na.rm = T),
            wid_med = median(fishing_area_width, na.rm = T))

d_by_sp  
```



```{r}
ggplot(select(d_sum, fishing_area_length), aes(x=fishing_area_length)) +
  geom_histogram(position="identity", size = 0.75)+
  labs(x = "fishing_area_length", y = "#") +
  ggdark::dark_theme_bw(base_size = 11)

```

```{r}
ggplot(select(d_sum, fishing_area_width), aes(x=fishing_area_width)) +
  geom_histogram(position="identity", size = 0.75)+
  labs(x = "fishing_area_width", y = "#") +
  ggdark::dark_theme_bw(base_size = 11)

```

<br>

What do the small sites look like?  Should we keep them?

```{r}

length_cut <- 10
width_cut <- 1

sites_small <- d_sum %>%
  filter(fishing_area_length < length_cut |
           fishing_area_width < width_cut) %>% 
  mutate(wettedwidth_ave = rowMeans(select(., starts_with("wetted")), na.rm = TRUE)) %>% 
  select(fishing_area_length, fishing_area_width, wettedwidth_ave)

sites_small
```

<br>

These are small sites that have associated wetted widths

```{r}
sites_small %>% 
  filter(!is.na(wettedwidth_ave))
```

```{r}
sites_small_len <- sites_small %>% 
  filter(fishing_area_length < length_cut)

sites_small_len
```
<br>

Distribution of sites with small lengths 
```{r}
ggplot(select(sites_small_len, fishing_area_length), aes(x=fishing_area_length)) +
  geom_histogram(position="identity", size = 0.75)+
  labs(x = "fishing_area_length", y = "#") +
  ggdark::dark_theme_bw(base_size = 11)

```


<br>

Sites with small widths

```{r}
sites_small_wid <- sites_small %>% 
  filter(fishing_area_width < width_cut)

sites_small_wid
```

<br>

Distribution of sites with small widths.  Are these sites where it was a presence/absence test so maybe not suitable for density modelling? Don't know...
```{r}
ggplot(select(sites_small_wid, fishing_area_width), aes(x=fishing_area_width)) +
  geom_histogram(position="identity", size = 0.75)+
  labs(x = "fishing_area_width", y = "#") +
  ggdark::dark_theme_bw(base_size = 11)

```




