

# Make FISS data spatial
We need in spatial format to tie to the FWA so lets put everything in albers and add the X and Y to the dataframe

```{r}
d_sum_albers <- d_sum %>% 
  dplyr::group_split(utm_zone) %>% 
  map(utm_to_coord) %>% 
  bind_rows()
```

<br>

Burn to a csv so that Simon can access and join to habitat characteristics

```{r}
d_sum_albers %>% readr::write_csv(file = paste0(getwd(), '/data/fiss_density.csv'))
```

Next steps?:

 * While Joe and Nadine tweak the channel-width-21 analysis and have a look at what data from here they think we should keep or throw away...
 * Simon maybe burns dataframe into postgres that represents the X and Y locations of these sites and ties the locations of the sites to stream segments then pulls out everything he can about the watershed upstream (ex. elevation, watershed size, channel width, discharge, BEC zone, precip, etc ).  Future considerations include perhaps forest cover, geology, channel confinement, [Variable Infiltration Capacity (VIC-GL) model stuff](https://www.pacificclimate.org/data/gridded-hydrologic-model-output))
 * We should QA how well the sites tie to streams and find a way to filter out (or correct) bad matches if possible.
 * Feed results back to Joe and Nadine to see what we can gleen from the data.
