

# Make FISS data spatial
We need in spatial format to tie to the FWA so lets put everything in albers and add the X and Y to the dataframe

```{r}
d_sum_albers <- d_sum %>% 
  dplyr::group_split(utm_zone) %>% 
  map(utm_to_coord) %>% 
  bind_rows()
```

<br>

Burn to a csv so that Simon can access and join to habitat characteristics

```{r}
d_sum_albers %>% readr::write_csv(file = paste0(getwd(), '/data/fiss_density.csv'))
```

Next steps?:

 * burn dataframe into postgres that represents the X and Y locations of these sites
 * tie the locations of the sites to stream segments
 * QA how well the sites tie to streams and find a way to filter out (or correct) bad matches. I wonder about having a little script that will biuld a quick R map of the watershed showing the site, watershed, stream, elevation contours, etc - just an idea).  Might be quick and easy once set up but could be easier to just use Q...
 * extract habitat characteristics associated with the points (elevation, watershed size, channel width, discharge, BEC zone?, forest cover?, geology, channel confinement?)
